The impact of environmental shocks on children's schooling in Bolivia

### 2020-05-07 paper_draft.Rmd
created lagged variables

export_summary_table(dfSummary(flood_summary))
```
The drought data also spans the years 2005-2012 and shows the frequency of droughts in each municipality by year.

@@

>>>>

#lagged flood data created in excel
flood_lag <- read_csv(file.path("Raw data", "lagflood.csv"))
#library(DataCombine)
#flood_lags <- slide(flood_summary, Var = "floods", slideBy = -1)

flood_total <- flood_summary %>% 
  left_join(flood_lag)

export_summary_table(dfSummary(flood_total))

```
The drought data also spans the years 2005-2012 and shows the frequency of droughts in each municipality by year.

@@

#lagged drought data created in excel
#library(xlsx)
#write.xlsx(drought_summary, "C:\\Users\\katya\\Documents\\MyDocuments\\A Smith College Spring Semester\\Natural Resource Economics\\seminar-paper-katyagi21\\lagdrought.xlsx")

drought_lag <- read_csv(file.path("Raw data", "lagdrought.csv"))

drought_total <- drought_summary %>% 
  left_join(drought_lag)
